---
title: "615HW2"
date: "2022-09-26"
output:
  pdf_document: default
  
  'df_document: null': default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Fuel Economy
##1
```{r}
library(ggplot2)
setwd("~/Downloads")
vehicles <- read.csv('vehicles.csv')
vehicles$phevBlended <- as.logical(vehicles$phevBlended)
v1 <- subset(vehicles,select=c("fuelCost08","make","mpgData","year","phevBlended","city08","highway08"))
v2 <- subset(v1,phevBlended == FALSE)
summary(v2)
ggplot(data = v2,aes(x=year,y=fuelCost08))+
  geom_point(color="black",pch=20,size=2)+
  geom_smooth(color="orange",method = 'gam')+
  labs(
    x="40 year span 1984 through 2023",
    y="Annual fuel cost",
    title=" Change of annual fuel cost over 40 years "
  )

```

##2
```{r}
v3 <- subset(v1,make==c("Ferrari","Toyota","Volvo","Audi"))
ggplot(data=v3,aes(x=year,y=city08,group=make,color=make))+
  geom_line(size=2)+
  labs(
    x="40 year span 1984 through 2023",
    y="citympg",
    title="Change of citympg over 40 years"
  )
```
```{r}
ggplot(data=v3,aes(x=year,y=highway08,group=make,color=make))+
  geom_line(size=2)+
  labs(
    x="40 year span 1984 through 2023",
    y="highwaympg",
    title="Change of highwaympg over 40 years"
  )

```
Among the selected makes, Toyota is the one which has made the great progress. 

## NASDAQ Composite
```{r}
setwd("~/Downloads")
IXIC2122 <- read.csv('IXIC21-22.csv')
library(ggplot2)
library(tidyverse)
library(tidyquant)
tq_get_options()
ggplot(data=IXIC2122,aes(x = Date, y =  Close)) +
geom_candlestick(aes(open = Open, high = High, low = Low, close = Close)) +
labs(title = "NASDAQ Candlestick Chart", y = "Close", x = "Date") +
theme_tq()

```


## Rural Capacity Index
##1
```{r}
setwd("~/Downloads")
rci <- read.csv('ruralCapacityData.csv')
rci1 <- subset(rci,County !="Bernalillo County")
ggplot(data=rci1,aes(x=per_fam_below_pov,y=cap_index))+
  geom_point(color="purple",pch=20,size=3)+
  geom_smooth(method = 'loess',formula="y~x",span=0.5)+
  labs(
    x="Percentage of families below the poverty level",
    y="Rural Capacity Index",
    title="RCI - Percentage of families below the poverty level")

```
Explanation: Relationship between RCI and percentage of families below the poverty level. 

##2
```{r}
ggplot(data=rci1,aes(x=per_over_25_with_bach,y=cap_index))+
  geom_point(color="blue",alpha=0.5,pch=20,size=3)+labs(
    x="Percent of population 25 and over with a bachelors degree",
    y="Rural Capacity Index",
    title="Number of houses with broadband - per_over_25_with_bach"
  )
```
Explanation:A scatter plot indicating the relationship between the number of houses with broadband and the percent of adults, 25 and older, with bachelor degrees.


##3-1
```{r}
rci_1 <- subset(rci1,pop_total<16000)
ggplot(data=rci_1,aes(x=pop_total,y=cap_index))+
  geom_point(color="red",pch=5,size=5)+
  geom_smooth(method="loess",formula=y~x,span=0.4)+
  labs(
    x="Total population below 16k",
    y="Rural Capacity Index",
    title="Total population below 16k - Rural Capacity Index"
  )
```
Explanation:Relationship between RCI and population for population below 16k.


##3-2
```{r}
rci_2 <- subset(rci1,16000<pop_total & pop_total<55000)
ggplot(data=rci_1,aes(x=pop_total,y=cap_index))+
  geom_point(color="red",pch=5,size=5)+
  geom_smooth(method="loess",formula=y~x,span=0.4)+
  labs(
    x="Total population between 16k and 55k",
    y="Rural Capacity Index",
    title="Total population between 16k and 55k - Rural Capacity Index"
  )
```
Explanation:Relationship between RCI and population for population between 16k and 55k. 


##3-3
```{r}
rci_3 <- subset(rci1,pop_total>55000)
ggplot(data=rci_1,aes(x=pop_total,y=cap_index))+
  geom_point(color="red",pch=5,size=5)+
  geom_smooth(method="loess",formula=y~x,span=0.4)+
  labs(
    x="Total population above 55k",
    y="Rural Capacity Index",
    title="Total population above 55k - Rural Capacity Index"
  )
```

Explanation:Relationship between RCI and population for population above 55k. 